\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{LUMP: Locking and Unlocking Mobile Platform}

### 2013-05-05 paper.tex
Added a citation

Furthermore, more features such as distributable, expiring keys could be implemented to be used by establishments such as hotels, bed and breakfasts, and hosts on sites such as Airbnb. Perhaps a separate app for owners of such establishments would be the ideal way to implement such a solution. A distribution system like this could greatly simplify the problem of keeping track of external keys. Extending the stay of a particular visitor would be as easy as changing a number in an admin console or mobile app. Bed and breakfast owners could also revoke keys remotely, as well as check the status of particular doors in the hotel (to see if one was left unlocked, for example).\\

@@

\end{thebibliography}

>>>>

Furthermore, more features such as distributable, expiring keys could be implemented to be used by establishments such as hotels, bed and breakfasts, and hosts on sites such as Airbnb \cite{airbnb}. Perhaps a separate app for owners of such establishments would be the ideal way to implement such a solution. A distribution system like this could greatly simplify the problem of keeping track of external keys. Extending the stay of a particular visitor would be as easy as changing a number in an admin console or mobile app. Bed and breakfast owners could also revoke keys remotely, as well as check the status of particular doors in the hotel (to see if one was left unlocked, for example).\\

@@

\bibitem{airbnb}
"Airbnb." Airbnb. \url{https://www.airbnb.com/} (accessed May 4, 2013).
\end{thebibliography}
